%% uctest.tex 11/3/94
%% Copyright (C) 1988-2004 Daniel Gildea, BBF, Ethan Munson.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2003/12/01 or later.
%
% This work has the LPPL maintenance status "maintained".
% 
% The Current Maintainer of this work is Daniel Gildea.
%
% 2007/08/01
% LaTeX Package "ucr" is modified from LaTeX package "ucthesis."
% This modification is therefore under to the conditions of 
% the LaTeX Project Public License.
% Its formality is suitable for the dissertation of Universty of
% California, Riverside.
% This test document is for the convenience of all students of
% Universty of California, Riverside.
% Contact Charles Yang at chcyang@yahoo.com if you like.
% Charles Yang has nothing to do with the original author's sarcasm.
%
% \documentclass[11pt]{ucthesis}
% \documentclass[11pt]{ucr}
\documentclass[oneside,final, letterpaper]{ucr}

\usepackage[english]{babel}
\usepackage{blindtext}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{algorithm, algorithmic}
%\usepackage{algorithmic}
\usepackage{subcaption,xcolor}
\usepackage{comment}
%\usepackage{gensymb}
%\usepackage[hyphens]{url}
%\usepackage{breakurl}
%\def\UrlBreaks{\do\/\do-}
\usepackage[breaklinks]{hyperref}
\usepackage{bbding}
%\usepackage{times}
%\usepackage[colorlinks]{hyperref}
%\hypersetup{citecolor=black,linkcolor=black}
%\usepackage{longtable}

\usepackage{pgffor}
\usepackage{listings}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstset
{ %Formatting for code in appendix
    %language=Matlab,
    %basicstyle=\scriptsize,
    basicstyle=\scriptsize,
    backgroundcolor=\color{backcolour},
    numbers=left,
    stepnumber=1,
    showstringspaces=false,
    tabsize=1,
    breaklines=true,
    breakatwhitespace=false,
    numbersep=2pt,
    keepspaces=true,
    xleftmargin=1.3em,
    %frame=single,
    framexleftmargin=1.3em
}

\definecolor{groovyblue}{HTML}{0000A0}
\definecolor{groovygreen}{HTML}{008000}
\definecolor{darkgray}{rgb}{0,0,0}
 
\lstdefinelanguage{Groovy}[]{Java}{
  keywordstyle=\color{groovyblue}\bfseries,
  stringstyle=\color{black}\ttfamily,
  keywords=[3]{each, findAll, groupBy, collect, inject, eachWithIndex, input, section, preferences, title, required, multiple, options},
  morekeywords={def, as, in, use},
  moredelim=[is][\textcolor{darkgray}]{\%\%}{\%\%},
  moredelim=[il][\textcolor{darkgray}]{§§}
}


% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{xspace}
\newcommand{\sys}{\mbox{\textsc{IotSan}}\xspace}
\newcommand{\spin}{\mbox{\textsc{Spin}}\xspace}

\newcommand{\PP}[1]{
\vspace{2px}
\noindent{\bf {#1}}
}

\newcommand{\etal}{\textit{et al}.\xspace}
\newcommand{\ie}{\textit{i}.\textit{e}.}
\newcommand{\eg}{\textit{e}.\textit{g}.}

\newcommand{\zhiyun}[1]{\textcolor{red}{[Zhiyun: #1]}}
\newcommand{\krish}[1]{\textcolor{blue}{[Srikanth: #1]}}
\newcommand{\chengyu}[1]{\textcolor{red}{[Chengyu: #1]}}
\newcommand{\thomas}[1]{\textcolor{violet}{[Thomas: #1]}}

\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}      \setlength{\parsep}{3pt}
      \setlength{\topsep}{3pt}       \setlength{\partopsep}{0pt}
      \setlength{\leftmargin}{1.0em} \setlength{\labelwidth}{1em}
      \setlength{\labelsep}{0.5em} } }
\newcommand{\squishend}{
    \end{list}  }
   
\newcommand{\squisholist}{
        \begin{enumerate}
                { \setlength{\itemsep}{0pt}      \setlength{\parsep}{0pt}
                        \setlength{\topsep}{0pt}       \setlength{\partopsep}{0pt}
                        \setlength{\leftmargin}{0em} \setlength{\labelwidth}{0em}
                        \setlength{\labelsep}{0em} } }
        \newcommand{\squishendo}{
        \end{enumerate}  }

\begin{document}


% Declarations for Front Matter

\title{Towards Fortifying the Safety and Security of IoT Systems}
\author{Dang Tu Nguyen}
\degreemonth{December}
\degreeyear{2018}
\degree{Master of Science}
\chair{Dr. Srikanth V. Krishnamurthy}
\othermembers{Dr. Chengyu Song\\
Dr. Zhiyun Qian}
\numberofmembers{3}
\field{Computer Science}
\campus{Riverside}

\maketitle
\copyrightpage{}
\approvalpage{}

\degreesemester{Fall}

\begin{frontmatter}

\begin{acknowledgements}
The research, writing and completion of this thesis are impossible without
many individuals' generosity in their support and assistance. First, I would like to offer
my special thanks to my committee for their inspirations, critical feedbacks, and
suggestions. My greatest gratitude goes to my advisor, Dr. Srikanth V. Krishnamurthy, and my co-advisors, Dr. Chengyu Song and Dr. Zhiyun Qian. Their tireless mentoring, patience and encouragement have supported and guided me through
this difficult but exciting process. Moreover, their critical insight helped to shape my
perspective and theoretical framework on this research project. They also
demonstrated to me on how to be a responsible and professional researcher.

This research project had been supported by numerous
scholarships and grants. My studies had been founded by the graduate Fellowship from UCR and the U.S. Army Research Laboratory Cyber Security Collaborative Research Alliance.  I would not have this research completed without these supports.  Therefore, I would like to express my sincere thanks to UCR and the U.S. Army Research Laboratory.

Finally, I owed my deepest gratitude to my family for their support. My parents, my wife, and my son have been offering me their loving encouragements during my long years
of study and research. I am especially grateful to my wife for
her sacrifice and support to allow me to focus on my research and study.  
\end{acknowledgements}

\input{absm}

\tableofcontents
\listoffigures
\listoftables
\end{frontmatter}

% \part{First Part}


\input{introm}
\input{backm}
\input{scopem}
\input{overviewm}
\input{depm}
\input{transm}
\input{setm}
\input{modelm}
\input{outputm}
\input{evalm}
\input{discm}
\input{relatedm}
\input{concm}



\nocite{*}
% \singlespacing
% \bibliographystyle{alpha}
\bibliographystyle{plain}
%\bibliographystyle{./bibtex/ACM-Reference-Format}
\bibliography{./bibtex/mybibfile}

\input{appendix}


\end{document}
